A Decentralized Pub/Sub System for Trusted Machine Economy

### 2020-05-15 paper.tex
Modify Background MAM

\subsection{Masked Authenticated Messaging}
MAM resolves the challenge of publishing authenticated streaming data as zero-value transactions to IOTA ledger, and provides the ability to publish and fetch encrypted messages over the Tangle along with data integrity and access control. With MAM, the rights of data access is traded instead of a copy of data itself, which eliminates the need for data consumers to have additional storage.

In the IOTA protocol, \textbf{seed} is the identifier of its owner. An IOTA seed represents the ownership of all things associated with the user in the IOTA ecosystem, such as IOTA tokens or messages on the Tangle. With the seed, the owner can produce addresses and signatures in order to issue transactions or publish messages to MAM channels and endpoints.

Either channel or endpoint is like a singly-linked list. The MAM channel ID and endpoint ID are the addresses of transaction and are the root of a channel and endpoint. Each address of a message can be derived from the previous one. A user can create multiple channels and multiple endpoints under the same channel. The messages can be encrypted with the session key and broadcasted in chronological order to the Tangle by attaching it to an endpoint. This allows only entities that know the session key to be able to decode these messages after retrieving them from the Tangle, and the singly-linked list structure implements the concept of forward secrecy, where anyone has no access to the data back from his/her entry point. Fig.~\ref{fig:mam_struct} shows the architecture of MAM.

@@

The authentication in MAM includes source and data authentication. Source authentication ensures that the message originates from the claimed owner, and data authentication ensures the integrity of the data from that sender. These are achieved through the Merkle signature scheme\cite{MSS} (MSS) which is a digital signature scheme based on Merkle Hash Trees and One-way hash functions. However, the size of Merkle Hash Trees should be fixed at start, which is the size of a channel and the endpoint is decided before creation. Thus, data providers need to firstly decide how to distribute data product into MAM channels or endpoints.

%to be modify
Data providers are the primary role to interact with the MAM. With a seed, a provider can start creating a channel and endpoint. As mentioned above, the length of a channel and an endpoint is fixed, thus providers need to decide the selling unit of data products according to their data type or pricing strategy. Also data providers can a make product preview which is public and not encrypted on MAM. In Fig.~\ref{fig:mam_struct}, a "central endpoint" means its endpoint's ID is the same as channel's ID. By attaching part of the product to central endpoint can give subscribers a quick preview with channel's ID only, and users can easily verify the content with digital signatures in messages. Then if the trade is established, providers can then give subscribers the encrypted endpoint and session key to subscribers.

The decentralized and fault-tolerant characteristic of distributed ledgers reduce the risks of centralized storage services, and the underlying IOTA network is scalable which withstands real-time data while increasing users all over the world. Moreover, the features of MAM make it an even better data storage which allows preserving streaming data while ensuring data integrity, proving data ownership to any participants and managing session keys of data. And through the access control and the protocol of MAM, participants are allowed to subscribe to the future data. This ensures that only service requester and selected provider are in possession of a key to decrypt and read the content of the MAM channel and therefore retrieve transaction data for audit.

While the operations of MAM are time-consuming, brokers are responsible not only for being the bridge between providers and subscribers, but also for all MAM related operations, such as channel creation and encrypted data publishing in our system. See Fig.~ \ref{fig:launching_product}.

>>>>

\subsection{Masked Authenticated Messaging}
MAM publishes authenticated streaming data as zero-value transactions to IOTA ledger and provides the ability to publish and fetch encrypted messages over the IOTA Tangle along with data integrity and access control. With MAM, the rights of data access are traded instead of a copy of data in the data marketplace, which eliminates the need for data consumers to have additional storage.

In the IOTA protocol, \textbf{seed} is the identifier of its owner. An IOTA seed represents the ownership of all things associated with the user in the IOTA ecosystem, such as IOTA tokens or messages on the Tangle. With the seed, the owner can create addresses and signatures in order to issue transactions or publish messages to MAM channels and endpoints.

Either channel or endpoint is like a singly-linked list. The singly-linked list structure implements the concept of forward secrecy, where no one has access to the data back from his/her entry point. Furthermore, each address of a message can be derived from the previous one, which enables data consumers to subscribe to future data by having the endpoint ID. A MAM channel/endpoint ID is the address of a transaction and the first message of a channel/endpoint. The central endpoint in Fig.~\ref{fig:mam_struct} means its endpoint ID is the same as channel ID.

A user can create multiple channels and endpoints, and the messages can be encrypted with the session key then broadcasted in chronological order to the Tangle by attaching it to an endpoint. This allows only authorized entities are able to decode these messages after retrieving them from the Tangle.

@@

The authentication in MAM includes two aspects: source and data. Source authentication ensures the message that originates from the claimed owner, and data authentication ensures the integrity of the data from that sender. These are achieved through the Merkle signature scheme\cite{MSS} (MSS) which is a digital signature scheme based on Merkle Hash Trees and One-way hash functions. However, the size of Merkle Hash Trees, that is, the size of a channel/endpoint should be determined at the start. Thus, data providers need to first decide how to distribute data products into MAM channels/endpoints before uploading data.

Using MAM as a data storage benefits from the scalability of the underlying IOTA network as well as the decentralized and fault-tolerant characteristic of distributed ledgers, which reduce the risks of centralized storage services.
